Efficient ancestry and mutation simulation with msprime 1.0

### 2021-11-19 paper.tex
Cut down bottlenecks section

We have implemented instantaneous bottlenecks in \msprime~1.0
using a variant of Hudson's linear time single-locus coalescent
algorithm~\citep{hudson1990gene}. Instantaneous bottlenecks are specified
by adding events to the \texttt{Demography} class
(see the \nameref{sec-demography} section)
and can be used in combination with any other demographic modelling
features. We have validated the results of these simulations by comparing
against analytical expectations for coalescence times and the
site frequency spectrum~\citep{bunnefeld2015inferring}.

>>>>

We have implemented instantaneous bottlenecks in \msprime~1.0
using a variant of Hudson's linear time single-locus coalescent
algorithm~\citep{hudson1990gene}, and
validated the results by comparing
against analytical expectations~\citep{bunnefeld2015inferring}.
